Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-22 longoutput.tex
Resolve TODOs on kernel intersections

\begin{definition}
	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n|U_i\in\set{I,X,Z}}$.
\end{definition}

@@

\begin{lemma}
	Some lemma on K clock and K prop
\end{lemma}

\begin{proof}
	Proof of above lemma
\end{proof}

Notice that (TODO Need proof)
$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{circuit}}}$$
We now consider the space outside the desired state.
$$S=(\spn\set{\ket{\psi_{circuit}}})^\bot$$
$$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
To combine the Hamiltonians, we apply the projection lemma twice.
$$\exists J_{clock}
=\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
=O(n)=O(T)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
$$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
=\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
TODO Here are some steps here that need to be spelled out
$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
\end{proof}

>>>>

\begin{definition}
	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n\colon U_i\in\set{I,X,Z}}$.
\end{definition}

@@

\begin{lemma}
	$$K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}\colon \ket{y}\in\mathcal{B}^{\otimes n}}$$
\end{lemma}

\begin{proof}
	Let $\ket\phi\in K_{clock}\cap K_{prop}$. As $\ket\phi\in K_{clock}$, the time register components are always valid unary representations. Now nonsider some $\tilde{t}$ such that $\ket\phi\bra{\tilde{t}}\ne0$. As $\ket\phi\in K_{prop}$, we can then say that $\ket\phi\bra{\tilde{t+1}}=U_{t+1}\ket\phi\bra{\tilde{t}}$ for $t\ne T$, and $\ket\phi\bra{\tilde{t}}=U_t\ket\phi\bra{\tilde{t-1}}$ for $t\ne0$. So we can obtain the required statement by induction.
\end{proof}

\begin{corollary}
	$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{circuit}}}$
\end{corollary}

We now consider the space outside the desired state.
$$S=(\spn\set{\ket{\psi_{circuit}}})^\bot$$
$$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
To combine the Hamiltonians, we apply the projection lemma twice.
$$\exists J_{clock}
=\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
=O(n)=O(T)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
$$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
=\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
\begin{align*}
	S\cap K_{clock}\cap K_{prop}&=S\cap\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}|\ket{y}\in\mathcal{B}^{\otimes n}}\\
	&=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}\colon\braket{x|y}=0}
\end{align*}
$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
\end{proof}
